\iflongcv
  \usepackage[margin=0.68in]{geometry}
\else
  \usepackage[margin=0.72in]{geometry}
\fi
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{etoolbox}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{needspace}

\definecolor{linkblue}{HTML}{165AA7}
\hypersetup{
  colorlinks=true,
  urlcolor=linkblue,
  linkcolor=linkblue,
  pdfauthor={Hayun Song},
  pdftitle={Curriculum Vitae - Hayun Song}
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\tabcolsep}{0pt}
\iflongcv
  \setlist{nosep,leftmargin=1.55em}
\else
  \setlist{nosep,leftmargin=1.5em}
\fi
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\iflongcv
  \fancyfoot[R]{\small H. Song, \thepage}
\fi
\fancypagestyle{plain}{%
  \fancyhf{}
  \renewcommand{\headrulewidth}{0pt}
  \iflongcv
    \fancyfoot[R]{\small H. Song, \thepage}
  \fi
}

\newcommand{\cvsection}[1]{%
  \iflongcv
    \Needspace{4\baselineskip}%
    \vspace{0.72em}%
    {\large\bfseries\MakeUppercase{#1}}\par
    \vspace{1.5pt}\hrule\vspace{5pt}%
  \else
    \Needspace{3\baselineskip}%
    \vspace{0.55em}%
    {\normalsize\bfseries\MakeUppercase{#1}}\par
    \vspace{1pt}\hrule\vspace{4pt}%
  \fi
}

\newcommand{\datedentry}[3]{%
  \begin{tabularx}{\linewidth}{@{}>{\raggedright\arraybackslash}X >{\raggedleft\arraybackslash}p{1.35in}@{}}
    #1 & #3
  \end{tabularx}\par
  \ifstrempty{#2}{}{{\small\hspace*{1.8em}#2\par}}%
}

\newcommand{\paper}[2]{\item #1. \emph{#2}.}
\newcommand{\abstracttext}[1]{%
  \iflongcv
    \par\vspace{3pt}\hspace*{0.9em}\begin{minipage}{0.965\linewidth}
      \small\textbf{Abstract:} #1
    \end{minipage}\par\vspace{4pt}
  \fi
}

\begin{document}

\begin{center}
  \iflongcv
    {\LARGE\bfseries HAYUN SONG}\par
    \vspace{4pt}
    {\normalsize Associate Research Fellow}\par
    {\normalsize International Macroeconomics Team}\par
    {\normalsize Department of International Macroeconomics and Finance}\par
    {\normalsize Korea Institute for International Economic Policy (KIEP)}\par
    \vspace{2pt}
    {\small Updated July 2026}
  \else
    {\LARGE\bfseries HAYUN SONG}\par
    \vspace{3pt}
    {\normalsize Associate Research Fellow, International Macroeconomics Team}\par
    {\normalsize Korea Institute for International Economic Policy (KIEP)}\par
    \vspace{3pt}
    {\small
      \href{mailto:hayunsong@kiep.go.kr}{hayunsong@kiep.go.kr}
      \quad\textbar\quad
      \href{https://hayunsong.com}{hayunsong.com}
      \quad\textbar\quad
      \href{https://www.linkedin.com/in/hayunsong}{LinkedIn}
    }
  \fi
\end{center}

\iflongcv
\cvsection{Contact Information}
\begin{tabularx}{\linewidth}{@{}X X@{}}
  KIEP, Sejong, Republic of Korea & Email: \href{mailto:hayunsong@kiep.go.kr}{hayunsong@kiep.go.kr} \\
  370 Sicheong-daero, Sejong-si 30147 & Tel: +82-44-414-1132 \\
  Web: \href{https://hayunsong.com}{hayunsong.com} & LinkedIn: \href{https://www.linkedin.com/in/hayunsong}{linkedin.com/in/hayunsong}
\end{tabularx}
\fi

\cvsection{Professional Experience}
\iflongcv
\datedentry{\textbf{Associate Research Fellow}, Korea Institute for International Economic Policy (KIEP)}{International Macroeconomics Team, Department of International Macroeconomics and Finance}{Aug. 2024--Present}
\else
\datedentry{\textbf{Associate Research Fellow}, Korea Institute for International Economic Policy (KIEP)}{}{Aug. 2024--Present}
\fi

\cvsection{Education}
\iflongcv
\datedentry{\textbf{Ph.D., Economics}, University of Southern California, CA, US}{}{2024}
{\small\hspace*{1.8em}\emph{High-dimensional Bayesian nonparanormal dynamic conditional model with multivariate volatility applications}\par}
{\small\hspace*{1.8em}Committee: M. Hashem Pesaran (Chair), Cheng Hsiao, Timothy Armstrong\par}
\datedentry{\textbf{M.S., Economics}, University of Wisconsin--Madison, WI, US}{}{2016}
\datedentry{\textbf{M.A., Economics}, Boston University, MA, US}{}{2014}
\datedentry{\textbf{B.A., Economics}, Sungkyunkwan University, Seoul, South Korea}{}{2012}
\datedentry{\textbf{B.A., Business Administration}, Sungkyunkwan University, Seoul, South Korea}{}{2012}
\else
\datedentry{\textbf{Ph.D., Economics}, University of Southern California}{Advisor: \href{http://www.econ.cam.ac.uk/people/emeritus/mhp1}{M. Hashem Pesaran}}{2024}
\datedentry{\textbf{M.S., Economics}, University of Wisconsin--Madison}{}{2016}
\datedentry{\textbf{M.A., Economics}, Boston University}{}{2014}
\datedentry{\textbf{B.A., Economics and Business Administration}, Sungkyunkwan University}{}{2012}
\fi

\cvsection{Fields of Interest}
Econometrics, Applied Econometrics, Bayesian Statistics

\cvsection{Research Papers}
\iflongcv
\begin{enumerate}[itemsep=0.42em]
\else
\begin{enumerate}[itemsep=0.4em]
\fi
  \paper{Song, Hayun (2024)}{High-dimensional Bayesian nonparanormal dynamic conditional model with multivariate volatility applications}
  \abstracttext{This paper develops a Bayesian method for estimating large conditional precision matrices within a DCC--GARCH framework. Wishart likelihoods, horseshoe priors, and a nonparanormal rank transformation allow sparse conditional dependence estimation even when the number of variables exceeds the number of observations. Monte Carlo experiments and applications to international stock indices and asset-pricing models demonstrate the method's empirical usefulness.}

  \item Lee, Junghyuk and Hayun Song (2023). \emph{Female labor force participation and gender role attitudes}. [Manuscript in preparation].

  \paper{Song, Hayun (2021)}{Bayesian dynamic factor augmented structure learning: cross-sectional dependence for residuals}
  \abstracttext{This paper proposes a Bayesian dynamic factor-augmented VAR that represents contemporaneous cross-sectional dependence as a graphical model. Factors are estimated through principal components and forward-filtering backward-sampling, while rescaled spike-and-slab priors address high-dimensional transition matrices. A fractional Bayes factor supports graphical model selection, with simulations and an application to U.S. house prices illustrating the approach.}

  \paper{Song, Hayun (2018)}{Individual heterogeneity in the returns to schooling: instrumental variable quantile regression}
  \abstracttext{Using instrumental variable quantile regression on twins data, this paper studies heterogeneity in returns to schooling while addressing ability and measurement-error biases. Estimated returns range from 9 to 15 percent across quantiles, and Wald-type location-shift tests provide evidence of individual heterogeneity. The analysis also examines ability bias, measurement error, linearity, and heterogeneous returns to other worker characteristics.}
\end{enumerate}

\iflongcv
\cvsection{KIEP Policy Research and Publications}
\begin{enumerate}[series=kieppubs,itemsep=0.48em]
  \item Hayun Song and Munsu Kang (2026). \href{https://www.kiep.go.kr/gallery.es?act=view\&bid=0003\&list_no=12327\&mid=a10102020000}{\emph{Oil Price Shocks from the U.S.-Iran War: Spillover Effects on Major Economies}}. KIEP Today's World Economy 26-09.
  \item Hayun Song and ByeongJun Lee (2026). \href{https://www.kiep.go.kr/gallery.es?act=view\&bid=0004\&list_no=12214\&mid=a10102030000}{\emph{AI Usage in Major Economies and Korea}}. KIEP World Economy Focus 26-04.
  \item Hayun Song, Sang-Ha Yoon, and Youngdoo Cho (2026). \href{https://www.kiep.go.kr/gallery.es?act=view\&bid=0003\&list_no=12190\&mid=a10102020000}{\emph{Economic Spillovers of Major External Shocks: Trade Policy Uncertainty and Oil Prices}}. KIEP Today's World Economy 26-03.
  \item Jiyoung Moon, Hayun Song, Hong Won Kim, JiWon Choi, and Ko Un Cho (2025). \href{https://www.kiep.go.kr/gallery.es?act=view\&bid=0001\&list_no=12325\&mid=a10101200000}{\emph{China's Medium- and Long-Term Growth Outlook and Changes in Its Growth Structure}}. KIEP Basic Research Report 25-12.
  \item Hongseok Choi, Jee Won Park, Hayun Song, ByeongJun Lee, and Kotbee Shin (2025). \href{https://www.kiep.go.kr/gallery.es?act=view\&bid=0001\&list_no=12300\&mid=a10101200000}{\emph{Global Trends in High Debt Levels and Their Macroeconomic Implications}}. KIEP Basic Research Report 25-11.
  \item Jung Eun Yoon, Hayun Song, and Byungjun Lee (2025). \href{https://www.kiep.go.kr/gallery.es?act=view\&bid=0001\&list_no=12180\&mid=a20205040000}{\emph{Cross-Country Economic Spillover Effects of Intangible Asset: Technology Diffusion and Implications}}. KIEP Policy Analyses 25-01.
  \item Song, Hayun (2025). \href{https://www.kiep.go.kr/gallery.es?act=view\&bid=0008\&list_no=11935\&mid=a20205020000}{\emph{Small Differences, Large Divisions: How Political Gaps Widen Over Time}}. KIEP Opinions 319.
\end{enumerate}
\else
\cvsection{Selected KIEP Publications}
\begin{enumerate}[itemsep=0.32em]
  \item Hayun Song and Munsu Kang (2026). \href{https://www.kiep.go.kr/gallery.es?act=view\&bid=0003\&list_no=12327\&mid=a10102020000}{\emph{Oil Price Shocks from the U.S.-Iran War: Spillover Effects on Major Economies}}. KIEP Today's World Economy 26-09.
  \item Hayun Song and ByeongJun Lee (2026). \href{https://www.kiep.go.kr/gallery.es?act=view\&bid=0004\&list_no=12214\&mid=a10102030000}{\emph{AI Usage in Major Economies and Korea}}. KIEP World Economy Focus 26-04.
  \item Hayun Song, Sang-Ha Yoon, and Youngdoo Cho (2026). \href{https://www.kiep.go.kr/gallery.es?act=view\&bid=0003\&list_no=12190\&mid=a10102020000}{\emph{Economic Spillovers of Major External Shocks: Trade Policy Uncertainty and Oil Prices}}. KIEP Today's World Economy 26-03.
  \item Hongseok Choi, Jee Won Park, Hayun Song, ByeongJun Lee, and Kotbee Shin (2025). \href{https://www.kiep.go.kr/gallery.es?act=view\&bid=0001\&list_no=12300\&mid=a10101200000}{\emph{Global Trends in High Debt Levels and Their Macroeconomic Implications}}. KIEP Basic Research Report 25-11.
\end{enumerate}
\fi

\cvsection{Fellowships, Honors, and Awards}
\iflongcv
\datedentry{\textbf{Summer Research Award}, Department of Economics, USC}{Best third-year paper award.}{2021}
\datedentry{\textbf{Summer Research Award}, Department of Economics, USC}{Best second-year paper award.}{2018}
\datedentry{\textbf{Scholarship for Excellence}, Sungkyunkwan University}{Awarded to the top 50 students in the department.}{2009}
\else
\datedentry{\textbf{Summer Research Award}, Department of Economics, USC}{}{2021, 2018}
\datedentry{\textbf{Scholarship for Excellence}, Sungkyunkwan University}{}{2009}
\fi

\iflongcv
\cvsection{Research and Teaching Assistance}
\datedentry{\textbf{Research Assistant}, University of Southern California}{Prof. M. Hashem Pesaran, with Prof. Ron Smith}{Fall 2021--2024}
\datedentry{\textbf{Teaching Assistant}, University of Southern California}{}{}
{\small
\hspace*{1.8em}ECON 318: Introduction to Econometrics (undergraduate) \hfill Summer 2022, Spring 2022\par
\hspace*{1.8em}ECON 513: Practice of Econometrics (master's) \hfill Fall 2021\par
\hspace*{1.8em}ECON 611: Probability and Statistics for Economists (Ph.D.) \hfill Fall 2018\par
\hspace*{1.8em}ECON 401: Mathematical Methods in Economics (undergraduate) \hfill Fall 2018\par
\hspace*{1.8em}ECON 305: Intermediate Macroeconomic Theory (undergraduate) \hfill Fall 2017, Spring 2018\par
}

\cvsection{Data Analytic Projects}
\iflongcv
\begin{enumerate}[itemsep=0.44em]
\else
\begin{enumerate}[itemsep=0.28em]
\fi
  \item \textbf{LGBT Clinic Data Analysis} \hfill 2018
  \iflongcv\par{\small Analyzed clinic appointment and insurance data, identifying systematic differences in visit timing and insurance coverage across patient groups.}\fi
  \item \textbf{Anti-AgingGames.com Senior Center Cognitive Training Pilot Study} \hfill 2018
  \iflongcv\par{\small Assessed the relationship between game participation and word and digit memory scores, and proposed a new game design separating visual and auditory effects.}\fi
  \item \textbf{Psychology Evaluation of Fotonovela}, with Aviroop Ghosal \hfill 2018
  \iflongcv\par{\small Evaluated a photo-based educational tool for dementia knowledge and found significant gains in post-intervention and follow-up test scores relative to a standard brochure.}\fi
\end{enumerate}

\cvsection{Other Information}
\textbf{Military Service:} Corporal, Republic of Korea Army (ROKA) \hfill Feb. 2019--2020\par
\textbf{Programming Languages and Frameworks:} Python (CuPy, PyTorch), R, Stata, Gauss, Git, LaTeX, MATLAB, MySQL, Microsoft Office\par
\textbf{Languages:} English (Native Fluency), Japanese (Native Fluency), Korean (Native)\par
\textbf{Citizenship:} South Korea

\cvsection{References}
\begin{tabularx}{\linewidth}{@{}X X X@{}}
  \textbf{M. Hashem Pesaran} & \textbf{Cheng Hsiao} & \textbf{Timothy Armstrong} \\
  Distinguished Professor Emeritus & Professor of Economics & Professor of Economics \\
  University of Southern California & University of Southern California & University of Southern California \\
  \href{mailto:pesaran@usc.edu}{pesaran@usc.edu} & \href{mailto:chsiao@usc.edu}{chsiao@usc.edu} & \href{mailto:timothy.armstrong@usc.edu}{timothy.armstrong@usc.edu}
\end{tabularx}
\else
\cvsection{Skills and Languages}
\textbf{Programming:} Python (CuPy, PyTorch), R, Stata, Gauss, Git, LaTeX, MATLAB, and MySQL\par
\textbf{Languages:} Korean, English, and Japanese (native fluency)\par
\vspace{0.55em}
{\small Complete publication record, teaching experience, projects, and references are available in the \href{https://hayunsong.com/files/cv_hayunSong_long.pdf}{Long CV}.}
\fi

\end{document}
